---
title: "Google Trends Tiktok"
author: "Nazlı Ece Baltepe"
date: "04 10 2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(forecast)
library(ggplot2)
library(gtrendsR)
library(dplyr)
library(caret)
library(tidyverse)
library(ISLR)
library(broom)
library(lubridate)
```

#Pulling the data from Google Trends

Pulling the Google Trends data on the keyword "tiktok" via the gtrendsR package for the selected dates.

```{r}
tiktoktrends<-gtrends(keyword = c("tiktok"), time="2019-01-01 2022-10-02")
```

# Checking the structure

Checking the structure of the newly created object, tiktoktrends

```{r}
str(tiktoktrends)
```

# Pulling the data on the interest over time

Creating a new data frame with only data on the interest over time, and checking its structure.

```{r}
interestovertime<-tiktoktrends$interest_over_time
str(interestovertime)
```
# Creating the time series graph showing the change in interest over time

I will create the time series graph, zooming in the dates where the striking increase of the app's popularity started.

```{r}
interestovertime %>%
  ggplot(aes(x = date,
             y = hits,group=keyword,
             color = keyword))  +
  theme_bw()+
  labs(title = "Google Web searches for 'tiktok' from 2019 to 2022",
       caption = "Obs: 03/23, start of the increase of searches",
       x= NULL, y = "Interest")+
  ggforce::facet_zoom(xlim = c(as.POSIXct(as.Date("2020-03-01")),as.POSIXct(as.Date("2020-05-01")))) +
  geom_smooth(span=0.1,se=FALSE) + geom_vline(xintercept = as.POSIXct(as.Date("2020-03-23")),color = "red", lwd = 0.5,linetype="dashed")+
  theme(legend.position = "none") +
  geom_point(color="black")
  
```

Starting with the pandemic, there is a steady increase in the popularity of the app, as demonstrated in the Google trends information.

# Checking the linearity of the relationship between variables

Let's see if the relationship between the hits and date is linear.

```{r}
ggplot(data = interestovertime, aes(date, hits)) +
geom_point() + geom_smooth(method = "lm", se=FALSE)+
ggtitle("Linear Model Fitted to Data")
```

#Looking for a better model

The relationship does not seem completely linear. The pattern seems slightly non-linear. Let's compute the test error estimates for polynomials up to the 3rd degree, using the bootstrapping approach. I select 100 samples, and set the seed to 2.

```{r}
set.seed(2)
rmse <- numeric(3)
for(i in 1:3){
train_control <- trainControl(method = "boot",
number = 100)
f <- bquote(hits ~ poly(date, .(i)))
models <- train(as.formula(f), data = interestovertime,
trControl=train_control, method='glm')
rmse[i] <- models$results$RMSE
}

rmse
```
# Plotting the graph with the polynomial regression line

The model using the cubic function as has the lowest RMSE. I would like to see how this model fits on a graph first.

```{r}
ggplot(interestovertime, aes(date, hits)) +
geom_point() + geom_smooth(method = "lm", col="dodgerblue3",
formula=y~poly(x,3))+
ggtitle("Cubic Model Fitted to Data")
```
This model fits much better! 

# P value and the R-squared of the polynomial model

Let's see the P value and the R-squared value.

```{r}
model <- lm(hits ~ poly(date,3),data=interestovertime)
summary(model)
```
P value is below 0.05, indicating a statistical relationship between date and Google hits. The R-squared is 0.9681, which means that the model explains %96.81 of the variability in the response variable, which is hits. This indicates that the model has a high validity.

# Forecasting the future trend via auto.arima

auto.arima is a function in the forecast package which fits the best ARIMA model to our data. As it works only with univariate time series, I pull the hits data and turn it into time series before creating the model. Then, I plot the forecast for the next 100 steps, providing us the forecast until 2024.

```{r}
onlyhits<-ts(interestovertime$hits,start= c(2019,1,1), frequency= 52.14)
onlyhits
modelm<-auto.arima(onlyhits)
forecast_data<-forecast(modelm, 100)
plot(forecast_data, main = "Forecasting Google Trends for Tiktok", ylab = "Hits", xlab = "Date") 
```
According to this forecast, the popularity of Tiktok will continue to increase in next couple of years.